Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-10 documentation/paper.tex
Added data for banded frequency with wall cuts

Very interestingly, $FourierMLP(\beta_{8})$ performed better than either $FourierMLP(PosCor(\beta{8}), \chi)$ or \\ $FourierMLPWithPos(\beta{8}, \chi)$, which produced accuracy values of 97\% and 95\%, respectively.

@@

@@

The following tables compare the accuracy and mean class-wise standard deviation values of various supervised learning configurations, with Acoustic Parameter and the original PICO-60 neural network provided as baselines.

>>>>

Very interestingly, $FourierMLP(\beta_{8})$ performed better than either $FourierMLP(PosCor(\beta_{8}), \chi)$ or \\ $FourierMLPWithPos(\beta{8}, \chi)$, which produced accuracy values of 97\% and 95\%, respectively.

@@

The following tables compare various multi-layer perceptron discriminators, with and without wall cuts.

\begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
    \hline
    $FourierMLP(PosCor(\beta_{8}))$ & 0 & 0.5 & 2 & 95\% & 0.56 \\
    \hline
    $FourierMLP(\beta_{8})$ & 0 & 0.5 & 2 & 98\% & 0.29 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.5 & 3 & 95\% & 0.44 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.25 & 3 & 97\% & 0.43 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0.003 & 0.25 & 3 & 93\% & 0.54 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 94\% & 0.52 \\
    \hline
\end{tabular}

@@

The following tables compare the accuracy and mean class-wise standard deviation values of various supervised learning configurations with multiple input formats, with Acoustic Parameter and the original PICO-60 neural network provided as baselines.
